%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
%\cvsection{Work Experience}
\cvsectionIcon{Work Experience}{\faBriefcase}

 \

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
    \cventry
    {Senior Developer} % Job title
    {Curtin Institute of Radio Astronomy} % Organization
    {Bentley, WA} % Location
    {Jan. 2021 - PRESENT} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Enabled researchers to apply novel analysis techniques at an unprecedented scale with a bespoke Nextflow pipeline.}
        \item {Developed a Rust application to preprocess correlator visibilities from the Murchison Widefield Array radio telescope, which significantly improved performance and reliability over its predecessor.}
        \item {Assisted in the development of a Rust application for GPU-accelerated calibration radio telescope data.}
        \end{cvitems}
    }

%---------------------------------------------------------
    \cventry
    {Developer Consultant} % Job title
    {ThoughtWorks} % Organization
    {Melbourne, VIC} % Location
    {Jan. 2019 - November 2020} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
        % \item {Lead a team of developers from around the world in building a VueJS web app for connecting victims of the Australian bushfire disaster with a searchable directory of helpful resources}
        \item {Assisted the Personalization and Optimization team at an airline with the productionisation of their machine learning pipelines}
        \item {Set up multiple Azure DevOps pipelines which provisioned a large retail organization's cloud infrastructure using Terraform.}
        \item {Built an augmented reality app for a major sporting organization.}
        \item {Helped a renewable energy company enrich the data visualizations in their React frontend and improve the test coverage of their GraphQL queries.}
        \item {Oversaw the security of multiple client engagements, facilitating threat modelling sessions and information security training.}
        \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Freelance IT Consultant} % Job title
    {Laserphile} % Organization
    {Melbourne, VIC} % Location
    {Jun. 2014 - Jan. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built a completely bespoke eCommerce system for a client with a dynamic and challenging set of requirements}
        \item {Created a set of utilities which could synchronize user, product and order data between a client's CRM, Accounting and eCommerce databases}
        \item {Learnt first-hand, the importance of rigid version control and testing procedures in collaborative software development projects}
        \item {Applied leadership skills to organize teams spanning multiple disciplines and timezones}
        \item {Gained an awareness of significance of good information security practices when administrating web-facing applications}
        \item {Took on the role of a sysadmin in an environment that was under a constant barrage of DDoS and attempted defacement attacks where I learnt pre-emptive DDoS mitigation techniques.}
        \item {Performed incident response for a client whose web hosting company and backups had been taken down by an advanced attacker.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {IT Infrastructure Manager} % Job title
    {Anna Chandler Design} % Organization
    {O'Connor, WA} % Location
    {Jan. 2010 - Jun. 2014} % Date(s)
    {
    \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Provided IT support and POS system deployment to a fleet of 4 stores}
        \item {Designed, Built and Optimized a custom WooCommerce website which has vastly improved the business’ sales.}
        \item {Installed and Maintained a network of security camera systems across multiple locations}
        \item {Created a utility which automatically synchronizes product stock data between WooCommerce and Xero using their respective APIs}
        \item {Built a custom map generator around the Xero accounting API}
    \end{cvitems}
    }

\end{cventries}
