%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
% \cvsection{Extracurricular Activity}
\cvsectionIcon{Hobbies and Extracurricular}{\faStar}
%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
%---------------------------------------------------------

\begin{cvparagraph}
In my spare time I play drums for two bands and make experimental electronic music using algorithmic composition. Writing music in high level languages like Supercollider, Haskell and Clojure/Overtone is a nice way to take a break from work. Most aspects of my life revolve around code in some way.
\end{cvparagraph}

\begin{cventries}

    \cventrysimple
        {Side Projects}
        {
            For most of my life, Python has been my native tongue, and I feel very much at home in a command line. I've used Python in countless open source projects ranging from small utilities and web scrapers to automate my workflow; to ambitious collaborative art projects for festivals. My friends and I have worked on several novel electronics engineering projects which we have written about in our blog. Here are some of the highlights:
        }
        {
            \begin{cvitems}
                \item {\subentrytitlestyle{Cortex} \acvSubItemSep Designed and implemented a custom serial protocol, client and server for synchronously transmitting pixel data to multiple microcontrollers as part of an interactive geodesic LED dome art project.}
                \item {\subentrytitlestyle{DARP} \acvSubItemSep Wrote a tool which generates alerts when a devices enters or leaves a network by analysing ARP packets.}
                \item {\subentrytitlestyle{Moonbuggy} \acvSubItemSep Programmed the Arduino firmware for an electric vehicle art project}
                \item {\subentrytitlestyle{Modified 3D Printer} \acvSubItemSep Designed custom components and firmware for a specialized 3d printer that could simultaneously print multiple materials}
            \end{cvitems}
        }

%---------------------------------------------------------

    \cventrysimple
        {Conferences / Workshops}
        {
            During my time as a freelancer, I've attented numerous conferences (at my own expense) because I love being at the forefront of research in the computer science and information security community. I watch the talks that come out of CCC, Black Hat and DEF CON religeously. Here are some of the recent conferences and workshops I've been a part of:
        }
        {
            \begin{cvitems}
                \item {\subentrytitlestyle{Platypus} \acvSubItemSep Ran a workshop on bypassing IoT security using UART, 2017}
                \item {\subentrytitlestyle{Ruxcon} \acvSubItemSep Melbourne, 2017}
                \item {\subentrytitlestyle{WAHCKon} \acvSubItemSep Perth, 2015 - 2016}
                \item {\subentrytitlestyle{PyCon} \acvSubItemSep Melbourne, 2017}
                \item {\subentrytitlestyle{Compose} \acvSubItemSep Melbourne, 2017 - 2018}
                \item {\subentrytitlestyle{PlatypusCamp} \acvSubItemSep Sydney, 2017}
                \item {\subentrytitlestyle{BuzzConf} \acvSubItemSep Melbourne, 2016 - 2017}
                \item {\subentrytitlestyle{WooConf} \acvSubItemSep San Francisco, 2014}
            \end{cvitems}
        }

    %---------------------------------------------------------

    \cventrysimple
        {Wargames / CTFs / Hackathons}
        {
            I started hacking with Kali Linux (or Backtrack as it was called then) in my teenage years on discarded computer hardware that I would find and repair. More recently I've been pursuing my passion in Infosec by competing in various capture the flag competitions, hackathons and wargame exercises.
        }
        {
            \begin{cvitems}
                \item {\subentrytitlestyle{PentesterLab Pro} \acvSubItemSep Essential \acvSubItemSep Unix \acvSubItemSep White \acvSubItemSep Intercept \acvSubItemSep Serialize}
                \item {\subentrytitlestyle{RuxCon CTF} \acvSubItemSep 2017}
                \item {\subentrytitlestyle{PlatypusCamp CTF} \acvSubItemSep Android Internals}
                \item {\subentrytitlestyle{PyCon Hackathon} \acvSubItemSep ESP32 Toolchain}
                \item {\subentrytitlestyle{ExploitExercises} \acvSubItemSep Nebula \acvSubItemSep Protostar}
                \item {\subentrytitlestyle{VulnHub} \acvSubItemSep Mr Robot}
                \item {\subentrytitlestyle{OverTheWire} \acvSubItemSep Bandit \acvSubItemSep Leviathan \acvSubItemSep Natas \acvSubItemSep Krypton}
            \end{cvitems}
        }

%---------------------------------------------------------
  \cventry
    {Participant} % Affiliation/role
    {ACM International Collegiate Programming Competition} % Organization/group
    {UWA} % Location
    {2010 - 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Vastly strengthened collaborative problem solving skills early on in my development career.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Member} % Affiliation/role
    {University Computer Club} % Organization/group
    {UWA} % Location
    {2010 - 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Developed unix and hacking skills in a collaborative environment}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
